### 2022-05-31 src/text/2-package-subsections/astro.tex
address bruno commnts

The gammapy.astro sub-package contains utility functions for studying physical scenarios in high energy astrophysics.
The dark matter module computes the so called J-factors and the gamma-ray spectra expected from annihilation of dark matter in different channels according to the recipe described in \cite{2011JCAP...03..051C}. In the source sub-module, dedicated classes exist for modeling galactic sources according to some come physical models, eg: SNR evolution models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the free expansion phase \citep{2006ARA&A..44...17G} or computation of physical parameters in a pulsar assumed to be a simple dipole. There are also dedicated tools for simulating synthetic populations based on physical models derived from observational or theoretical considerations for different classes of Galactic VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C}, pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y} and gamma-ray binaries. The gammapy.astro sub-package is currently incomplete in its description of physical scenarios, but since it works independently of the rest of the package, new classes can be added as an when required.

>>>>

The gammapy.astro sub-package contains utility functions for studying physical scenarios in high energy astrophysics.
The dark matter module computes the so called J-factors and the gamma-ray spectra expected from annihilation of dark matter in different channels according to the recipe described in \cite{2011JCAP...03..051C}. In the source sub-module, dedicated classes exist for modeling galactic sources according to some come physical models, eg: SNR evolution models \citep{1950RSPSA.201..159T, 1999ApJS..120..299T}, evolution of PWN during the free expansion phase \citep{2006ARA&A..44...17G} or computation of physical parameters in a pulsar assumed to be a simple dipole. There are also dedicated tools for simulating synthetic populations based on physical models derived from observational or theoretical considerations for different classes of Galactic VHE gamma-ray emitters: PWNe, SNRs \cite{1998ApJ...504..761C}, pulsars \cite{2006ApJ...643..332F, 2006MNRAS.372..777L, 2004A&A...422..545Y} and gamma-ray binaries. While the present list of use cases is rather preliminary, this can be enriched with time with by users and/or developers according to future needs.
